CFF GCT Study

### 2025-10-28 Christine Chan/CFF GCT Study/cff_gct_analysis.qmd
fixed Youden indices in dot plot

  geom_hline(yintercept = 91.5, linetype = "dashed", size = 1) +

@@

  geom_hline(yintercept = 140.5, linetype = "dashed", size = 1) +

@@

  geom_hline(yintercept = 97.5, linetype = "dashed", size = 1) +

@@

  geom_hline(yintercept = 161.5, linetype = "dashed", size = 1) +

@@

  geom_hline(aes(yintercept = 5.45, linetype = "Youden Index"), size = 1) +

>>>>

  geom_hline(yintercept = 94, linetype = "dashed", size = 1) +

@@

@@

  geom_hline(yintercept = 99, linetype = "dashed", size = 1) +

@@

  geom_hline(yintercept = 201, linetype = "dashed", size = 1) +

@@

  geom_hline(aes(yintercept = 5.5, linetype = "Youden Index"), size = 1) +
